Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments

### 2024-02-12 article/alt_article.qmd
ssss
sss

---
title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments 
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College
          city: Annandale-on-Hudson, NY
          country: USA

  - name: Leonardo Siles
    email: leonardo.siles@ucb.edu.bo
    affiliations:
        - id: ucb
          name: Universidad Católica Boliviana
          city: La Paz
          country: Bolivia
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: The World Bank                 
          city: Washington, D.C.
          country: USA
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.

>>>>

---
title: Estimating Quantile Regressions with Multiple Fixed Effects through Method of Moments 
author:
  - name: Fernando Rios-Avila
    email: friosavi@levy.org
    affiliations: 
        - id: levy
          name: Levy Economics Institute of Bard College
          city: Annandale-on-Hudson, NY
          country: USA          
    attributes:
      corresponding: true 
  - name: Leonardo Siles
    email: leonardo.siles@ucb.edu.bo
    affiliations:
        - id: ucb
          name: Universidad Católica Boliviana
          city: La Paz, Bolivia
  - name: Gustavo Canavire-Bacarreza
    email: gcanavire@worldbank.org
    affiliations:
        - id: wb
          name: The World Bank                 
          city: Washington, D.C.
          country: USA
abstract: |
  This paper proposes a new method to estimate quantile regressions with multiple fixed effects. The method, which expands on the strategy proposed by @mss2019, allows for the inclusion of multiple fixed effects and provides various alternatives for the estimation of standard errors. We provide Monte Carlo simulations to show the finite sample properties of the proposed method in the presence of two sets of fixed effects. Finally, we apply the proposed method to estimate the determinants of the surplus of government as a share of GDP, allowing for both time and country fixed effects.
